---
title: "Characterization of and selection on compound within-individual floral variation in *Vicia americana* (Fabaceae)"
author:
  - "Mason W. Kulbaba^[St. Mary's University, mason.kulbaba@stmu.ca, https://orcid.org/0000-0003-0619-7089]"
 
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  bookdown::pdf_document2:
    extra_dependencies: "amscd"
    number_sections: true
    toc: true
    toc_depth: 3
linkcolor: blue
urlcolor: blue
bibliography: vicia_refs.bib
#csl: journal-of-the-royal-statistical-society.csl
link-citations: true
---

# Abstract {-}

This document provides code to reproduce all results from the manuscript `Characterization of and selection on compound within-individual floral variation in *Vicia americana* (Fabaceae)`. The data file `vicia_final_data.csv` contains all data required to reproduce all results in the manuscript, and is located in the associated Zenodo repository. This study sought to describe the floral traits of *Vicia americana* as compound function-valued traits, and compare standardized linear selection estimates (e.g., $\beta$) as per @lande_measurement_1983, with the functional regression approached used by @kulbaba_inflorescence_2017 and @harder_dynamic_2019. 

# R

 * The version of R used to make this document is `r getRversion()`.

 * The version of the `rmarkdown` package used to make this document is
   `r packageVersion("rmarkdown")`.

 * The version of the `bookdown` package used to make this document is
   `r packageVersion("bookdown")`.

 * The version of the `dplyr` package used to make this document is
   `r packageVersion("dplyr")`.

 * The version of the `glmmTMB` package used to make this document is
   `r packageVersion("glmmTMB")`.

 * The version of the `DHARMa` package used to make this document is
   `r packageVersion("DHARMa")`.

 * The version of the `car` package used to make this document is
   `r packageVersion("car")`.

 * The version of the `caret` package used to make this document is
   `r packageVersion("caret")`.

 * The version of the `Hmisc` package used to make this document is
   `r packageVersion("Hmisc")`.
   
 * The version of the `tidyr` package used to make this document is
   `r packageVersion("tidyr")`.
   
 * The version of the `viridis` package used to make this document is
   `r packageVersion("viridis")`.
   
 * The version of the `refund` package used to make this document is
   `r packageVersion("refund")`.
   
* The version of the `mgcv` package used to make this document is
   `r packageVersion("mgcv")`.
   
* The version of the `tibble` package used to make this document is
   `r packageVersion("tibble")`.
   
Attach packages.
```{r package}

suppressMessages(library("dplyr"))
suppressMessages(library("glmmTMB"))
suppressMessages(library("ggplot2"))
suppressMessages(library("DHARMa"))
suppressMessages(library("car"))
suppressMessages(library("caret"))
suppressMessages(library("Hmisc"))
suppressMessages(library("tidyr"))
suppressMessages(library("viridis"))
suppressMessages(library("refund"))
suppressMessages(library("mgcv"))
suppressMessages(library("tibble"))
```

# Data

Load data file
```{r aster-version}
data<- read.csv("vicia_final_data.csv")
```

where the variables are

 * `PlantID` is a unique numerical identifier for each individual in the study (1-40).

 * `Branch` is a unique numerical identifier for each sequentially produced raceme (1-10).
  The first raceme to flower was designated as 1, and was the most basal. 

 * `PosSeq` is the sequential flower position (1-49) across all sequentially flowering racemes.

 * `BPos` is a composite of `Branch` and `Pos` (see below), indicating the raceme-specific 
  flower position.

 * `Pos` is the individual flower position within each raceme.
 
 * `FL` is the length of flower.
  
 * `FD` is the diameter of the flower where the banner petal attaches.
   
 * `B` is the length (height) of the banner petal.
 
 * `Date` is the date of flower opening, and when the three floral measurements were made.
 
 * `flw_date` is the numerical day of the flowering season (1-17) the flower opened.
 
 * `FlwFate` is whether or not a flower produced fruit (0 = no, 1 = yes).
 
 * `seeds` is the number of seed produced in a given fruit. 
 
 * `aborted` is the number of aborted embryos.
 
 * `unfert` is the number of unfertilized ovules.
 
 * `Notes` records any specific notes for a given flower. 
 
 * `flw_vol` is flower volume as approximated as a cone ($V = \frac{1}{3} \pi \frac{FD^2}{2} FL$)

# Standardized Linear Selection (e.g., @lande_measurement_1983)

## Relative fitness (seeds)
```{r calculate relative fitness per plant}

#make sure PlantID is a factor
data$PlantID<- as.factor(data$PlantID)

#calculate total seed set (fitness) at plant level
plant.seeds<- aggregate(data$seeds, by=list(data$PlantID), sum)

#reset column names
colnames(plant.seeds)<- c("PlantID", "tot_seeds")

#calculate relative fitness
plant.seeds$rel_seeds<- plant.seeds$tot_seeds/(mean(plant.seeds$tot_seeds, na.rm=T))

#Check
head(plant.seeds)
```

## Standardized traits
First need to calculate mean values for each floral trait, and then subtract the mean and divide by the trait standard deviation to standardize each traits for each individual plant. 
```{r standardize traits}
#First calculate mean trait value for each trait (yes, not efficient, but I like to see the steps)
mean.B<- aggregate(data$B, by=list(data$PlantID), mean, na.rm=T)
mean.B$Group.1 <- NULL
colnames(mean.B)<- "mean.B"

mean.FL<- aggregate(data$FL, by=list(data$PlantID), mean, na.rm=T)
mean.FL$Group.1 <- NULL
colnames(mean.FL)<- "mean.FL"

mean.FD<- aggregate(data$FD, by=list(data$PlantID), mean, na.rm=T)
colnames(mean.FD)<- c("PlantID", "mean.FD")

```

Merge into a single dataframe (I know this is not efficient, I like to see the steps) with relative seed set
```{r merge into one object}
traits<- cbind(mean.B, mean.FL, mean.FD)

# add relative seed set
sel.data<- merge(traits, plant.seeds)

#check
head(sel.data)

```


Now need to standardize individual plant mean (from above).
```{r standardize traits final}
#Calculate total (population) mean for each trait
sel.data$B_z<- (sel.data$mean.B - mean(sel.data$mean.B, na.rm = T))/sd(sel.data$mean.B, na.rm = T)
sel.data$FL_z<- (sel.data$mean.FL - mean(sel.data$mean.FL, na.rm = T))/sd(sel.data$mean.FL, na.rm = T)
sel.data$FD_z<- (sel.data$mean.FD - mean(sel.data$mean.FD, na.rm = T))/sd(sel.data$mean.FD, na.rm = T)

```



## Covariates
```{r aggregate covariates}
# total flowers
tot.flw<- aggregate(data$PosSeq, by=list(data$PlantID), max)
tot.flw$Group.1<- NULL

#total branches (racemes)
tot.branch<- aggregate(data$Branch, by=list(data$PlantID), max)
tot.branch$Group.1<- NULL
```

## Estimate ($\beta$)
Start with a poisson distribution. 
```{r linear selection estimates Poisson}
# model with standardized traits as fixed effects, and palntID as random  
# Fit Poisson model
fit_pois <- glmmTMB(rel_seeds ~ B_z + FL_z + FD_z, 
                    data = sel.data, family = poisson)

# Model diagnostics using DHARMa
sim_resid <- simulateResiduals(fit_pois, n = 1000)
plot(sim_resid)

# Test for overdispersion
testDispersion(sim_resid)

summary(fit_pois)


# Formal test for zero inflation
testZeroInflation(sim_resid) # not significant
```
The above model looks like a good fit (according to diagnostics), and not over dispersed. However, try fitting with a negative binomial distribution and compare AIC across two models.
```{r linear selection estimate Negative Binomial}
# Fit negative binomial model
fit_nb <- glmmTMB(rel_seeds ~ B_z + FL_z + FD_z, 
                    data = sel.data, family = nbinom2)

# Model diagnostics using DHARMa
sim_resid <- simulateResiduals(fit_nb, n = 1000)
plot(sim_resid)

# Test for overdispersion
testDispersion(sim_resid)

summary(fit_nb)

# Formal test for zero inflation
testZeroInflation(sim_resid) # not significant


AIC(fit_pois, fit_nb)
```
Both models fit well, and show the same pattern (significant effect of Banner height). As the AIC is slightly smaller with Poisson distribution, use this model.

Now produce a quick plot of the significant effect of banner height. A rather underwhelming figure.
```{r plotting selection gradient of banner height}

# Create prediction data over the range of standardized B
newdata <- data.frame(
  B_z = seq(min(sel.data$B_z), max(sel.data$B_z), length.out = 100),
  FL_z = 0,  # Hold other traits at their means (0 after standardization)
  FD_z = 0
)

# Predict expected seed number from the Poisson model
newdata$predicted_seeds <- predict(fit_pois, newdata, type = "response")

# Plot observed data and predicted curve
ggplot(sel.data, aes(x = B_z, y = tot_seeds)) +
  geom_point(alpha = 0.6, color = "gray30") +
  geom_line(data = newdata, aes(x = B_z, y = predicted_seeds), color = "blue", size = 1.2) +
  labs(
    x = "Standardized Banner Size (B)",
    y = "Seed Number (Fitness)",
    title = "Selection Gradient on Banner Size"
  ) +
  theme_minimal(base_size = 14)


```

# Floral Integration
Floral integration was described with correlation coefficients among floral traits. To explore if correlations among traits change across racemes, we compared correlation coefficients on racemes 1-5. To facilitate comparison among racemes, the first five flowers were used to calculate these correlations.
We calculated both within racemes (first five flowers), and among racemes (same position across first five racemes).
```{r correlations among floral traits}
# define function to extract, r, se, and P-value
get_cor_stats <- function(x, y) {
  ct <- cor.test(x, y, method = "pearson")
  r <- ct$estimate
  n <- sum(complete.cases(x, y))
  se <- sqrt((1 - r^2) / (n - 2))
  data.frame(correlation = r, se = se, p_value = ct$p.value)
}

```

## Withn raceme integration
Calculate within-inflorescence (raceme) floral integration.
```{r within raceme integration}
#within raceme integration
within_raceme <- data %>%
  filter(Branch %in% 1:5, Pos %in% 1:5) %>%
  group_by(Branch) %>%
  group_modify(~{
    df <- .
    bind_rows(
      get_cor_stats(df$FL, df$FD) %>% mutate(pair = "FL vs FD"),
      get_cor_stats(df$FL, df$B)  %>% mutate(pair = "FL vs B"),
      get_cor_stats(df$FD, df$B)  %>% mutate(pair = "FD vs B")
    )
  }) %>%
  ungroup() %>%
  select(Branch, pair, correlation, se, p_value)

within_raceme
```

Now make a nice little table with heatmap features to show pattern of floral integration with racemes, across the first five racemes.
```{r within-raceme integration table/map}
# prepare standard errors for inclusoin in table/heatmap
within_raceme <- within_raceme %>%
  mutate(sig = ifelse(p_value < 0.05, "*", ""),
         label = sprintf("%.2f\n(%.2f)%s", correlation, se, sig))

ggplot(within_raceme, aes(x = pair, y = factor(Branch), fill = correlation)) +
  geom_tile(color = "white") +
  geom_text(aes(label = label), color = "black", size = 4.2, lineheight = 0.9) +
  scale_fill_viridis(name = "Pearson r", limits = c(-1, 1)) +
  labs(
    title = "Trait Correlations Within First 5 Racemes",
    x = "Trait Pair", y = "Raceme (Branch #)",
    caption = "* indicates p < 0.001\n(SE shown in parentheses)"
  ) +
  theme_minimal(base_size = 13)
```


## Among raceme integration
```{r among raceme integration}
# among racemes
across_pos <- data %>%
  filter(Branch %in% 1:5, Pos %in% 1:5) %>%
  group_by(Pos) %>%
  group_modify(~{
    df <- .
    bind_rows(
      get_cor_stats(df$FL, df$FD) %>% mutate(pair = "FL vs FD"),
      get_cor_stats(df$FL, df$B)  %>% mutate(pair = "FL vs B"),
      get_cor_stats(df$FD, df$B)  %>% mutate(pair = "FD vs B")
    )
  }) %>%
  ungroup() %>%
  select(Pos, pair, correlation, se, p_value)

across_pos
```

Similar table as before, but now for same flower position (1-5) position across subsequently produced racemes.
```{r among-raceme integration table/map}
across_pos <- across_pos %>%
  mutate(sig = ifelse(p_value < 0.05, "*", ""),
         label = sprintf("%.2f\n(%.2f)%s", correlation, se, sig))

ggplot(across_pos, aes(x = pair, y = factor(Pos), fill = correlation)) +
  geom_tile(color = "white") +
  geom_text(aes(label = label), color = "black", size = 4.2, lineheight = 0.9) +
  scale_fill_viridis(name = "Pearson r", limits = c(-1, 1)) +
  labs(
    title = "Trait Correlations by Flower Position (Across Racemes)",
    x = "Trait Pair", y = "Flower Position",
    caption = "* indicates p < 0.001\n(SE shown in parentheses)"
  ) +
  theme_minimal(base_size = 13)
```
Floral integration at same flower position (1-5) across racemes (1-5) was moderate and consistent. However, floral integration within racemes disappeared with successive racemes for FL-FD and FD-B pairs. Only FL-B maintained a consistent and significant correlation. 

# Describe Subindividual Variation in Floral Traits
The goal is to describe the general pattern of within-individual floral trait variation, across all flower positions and racemes. Therefore, we will be using the variable `PosSeq` that describes the continuous flower position across all racemes on a plant. Generalized additive models (`gam`) from the package `mgcv` will be used to fit spline function to describe trait variation across continuous flower positions. 

First, need to standardize the flower positions within each plant. This is done as all plants do not have the same number of flowers. This will be important when applying functional regression, when the functional predictor has a variable domain. Note, we are using thin-plate splines, which are appropriate for variable domains. This will be ***required*** for functional regression, so it is appropriate to describe the patterns with the same basis type. Traditional b-splines have a standardized number of knots across all individuals, which is not appropriate when the number of data points across individuals is variable. Thin-plate splines (`bs="tp"`) allows for more flexibility (with an appropriate penalty) in knot placement, to accommodate the varible number of flowers across individual plants.  
```{r standardize flower positions}
dat <- data %>%
  group_by(PlantID) %>%
  mutate(pos_scaled = (PosSeq - min(PosSeq)) / (max(PosSeq) - min(PosSeq))) %>%
  ungroup()

dat$PlantID<- as.factor(dat$PlantID)
```

Next, fit GAM models for each trait across PosSeq using plant-specific smooths. 
```{r fit gam models}
# Flower Length (FL)
gam_FL <- gam(FL ~ s(pos_scaled, by = PlantID, bs = "tp") + PlantID, data = dat)



# Flower Diameter (FD)
gam_FD <- gam(FD ~ s(pos_scaled, by = PlantID, bs = "tp") + PlantID, data = dat)



# Banner height (B)
gam_B <- gam(B ~ s(pos_scaled, by = PlantID, bs = "tp") + PlantID, data = dat)

```

## Variation in individual plant trajectories 
The above shows that the GAM models describe significant within-individual variation in floral traits. Now see if individual plant trajectories (e.g., patterns of within-individual variation) significantly varies.

Start by fitting only global models (no individual plant effects).
```{r variation among plants}
# Model 1: Global spline only
mod_global.fl <- gam(FL ~ s(pos_scaled, bs="tp"), data = dat,
                  family = Gamma(link = "log"))

mod_global.fd <- gam(FD ~ s(pos_scaled, bs="tp"), data = dat,
                     family = Gamma(link = "log"))

mod_global.b <- gam(B ~ s(pos_scaled, bs="tp"), data = dat,
                    family = Gamma(link = "log"))

```

Now add individual plant effects.
```{r global + plant effects}
# Model 2: Global spline + plant-specific deviations
mod_plant.fl <- gam(FL ~ s(pos_scaled, bs="tp") + s(pos_scaled, by=PlantID, bs = "tp"), data = dat,
                 family = Gamma(link = "log"))

mod_plant.fd <- gam(FD ~ s(pos_scaled, bs="tp") + s(pos_scaled, by=PlantID, bs = "tp"), data = dat,
                    family = Gamma(link = "log"))

mod_plant.b <- gam(B ~ s(pos_scaled, bs="tp") + s(pos_scaled, by=PlantID, bs = "tp"), data = dat,
                   family = Gamma(link = "log"))
```

Now compare global and global + individual plant models
```{r model comparision}
# Compare models
anova(mod_global.fl, mod_plant.fl, test = "Chisq")
anova(mod_global.fd, mod_plant.fd, test = "Chisq")
anova(mod_global.b, mod_plant.b, test = "Chisq")
```
All three floral traits show significant differences among individual plant trajectories. 

Now include total flowers for each plant as a covariate. 
```{r compute total flowers}
# Compute total flowers per PlantID
dat <- data %>%
  group_by(PlantID) %>%
  mutate(total_flw = n()) %>%
  ungroup()

dat2 <- dat %>%
  group_by(PlantID) %>%
  mutate(pos_scaled = (PosSeq - min(PosSeq)) / (max(PosSeq) - min(PosSeq))) %>%
  mutate(total_flw = n()) %>%
  ungroup()

head(dat2)

```

Rerun models with covariate of total number of flowers.
```{r gam models with PlantID and total flowers}

mod.fl <- gam(FL ~ s(pos_scaled) + s(pos_scaled, by=PlantID, bs = "tp") + total_flw, 
           data = dat2,
           family = Gamma(link = "log"))

mod.fd <- gam(FD ~ s(pos_scaled) + s(pos_scaled, by=PlantID, bs = "tp") + total_flw, 
           data = dat2,
           family = Gamma(link = "log"))

mod.b <- gam(B ~ s(pos_scaled) + s(pos_scaled, by=PlantID, bs = "tp") + total_flw, data = dat2,
             family = Gamma(link = "log"))

```

Generate predicted values for plotting. Start with a grid to place predicted values.
```{r predicted values set up}
# Generate prediction grid
unique_plants <- unique(data$PlantID)

# Sequence of positions from 0 to 1 (because pos_scaled is standardized)
pos_grid <- seq(0, 1, length.out = 100)

# Total flower counts for each plant
plant_info <- dat2 %>%
  group_by(PlantID) %>%
  summarise(total_flw = first(total_flw))  # or n(), same result here

# Expand grid for predictions for each floral trait
newdata.fl <- expand_grid(
  PlantID = unique(data$PlantID),
  pos_scaled = pos_grid
) %>%
  left_join(plant_info, by = "PlantID")


newdata.fd <- expand_grid(
  PlantID = unique(data$PlantID),
  pos_scaled = pos_grid
) %>%
  left_join(plant_info, by = "PlantID")


newdata.b <- expand_grid(
  PlantID = unique(data$PlantID),
  pos_scaled = pos_grid
) %>%
  left_join(plant_info, by = "PlantID")
```

Now add predicted values from each trait-specific GAM model.
```{r add predicted values to grids}
newdata.fl$FL_pred <- predict(mod.fl, newdata = newdata.fl, type = "response")

newdata.fd$FD_pred<- predict(mod.fd, newdata = newdata.fd, type = "response")

newdata.b$B_pred<- predict(mod.b, newdata = newdata.b, type = "response")

```

Refit global GAM models (now with total flower number as covariate), and generate predicted values (use mean total flower number during prediction) for each floral trait.
```{r global GAM models with tot.flw and predcitions}
# 1. Global spline dataset (no PlantID)
mod_global <- gam(FL ~ s(pos_scaled) + total_flw, data = dat2,
                  family = Gamma(link = "log"))

global_data.fl <- data.frame(
  pos_scaled = pos_grid,
  total_flw = mean(dat2$total_flw)  # average value
)
global_data.fl$FL_pred <- predict(mod_global, newdata = global_data.fl, type = "response")



mod_global.fd <- gam(FD ~ s(pos_scaled) + total_flw, data = dat2,
                     family = Gamma(link = "log"))

global_data.fd <- data.frame(
  pos_scaled = pos_grid,
  total_flw = mean(dat2$total_flw)  # average value
)
global_data.fd$FD_pred <- predict(mod_global.fd, newdata = global_data.fd, type = "response")


mod_global.b <- gam(B ~ s(pos_scaled) + total_flw, data = dat2,
                    family = Gamma(link = "log"))

global_data.b <- data.frame(
  pos_scaled = pos_grid,
  total_flw = mean(dat2$total_flw)  # average value
)
global_data.b$B_pred <- predict(mod_global.b, newdata = global_data.b, type = "response")
```

Plot example of individual and global splines. Only showing plot for FL to save space. All data was written to .csv files, and plotted in SigmaPlot. Output .csv files for all three traits are found in the Results folder of the Zenodo repository. 
```{r show plot }
ggplot() +
  geom_line(data = newdata.fl, aes(x = pos_scaled, y = FL_pred, group = PlantID),
            color = "grey70", size = 0.6) +
  geom_line(data = global_data.fl, aes(x = pos_scaled, y = FL_pred),
            color = "black", size = 1.2) +
  labs(
    x = "Standardized Flower Position",
    y = "Predicted Flower Length (mm)",
    title = "Variation of Subindividual Flower Lenghth with Global Average"
  ) +
  theme_minimal()
```

# Coefficient of Variation 
Calculate mean, variance, and CV ($\frac{\sigma}{\bar{x}}$) for all traits. 
```{r calculate mean, var, and CV}
trait_stats <- data %>%
  group_by(PlantID) %>%
  summarise(
    FL_mean = mean(FL, na.rm = TRUE),
    FL_var  = var(FL, na.rm = TRUE),
    FL_cv   = sqrt(FL_var) / FL_mean,
    
    FD_mean = mean(FD, na.rm = TRUE),
    FD_var  = var(FD, na.rm = TRUE),
    FD_cv   = sqrt(FD_var) / FD_mean,
    
    B_mean  = mean(B, na.rm = TRUE),
    B_var   = var(B, na.rm = TRUE),
    B_cv    = sqrt(B_var) / B_mean
  )
```
## Variance and mean scaling
In order for CV to be informative, the mean must scale with the standard deviation. Therefore, perform a simple linear regression of trait variance on trait mean. See @herrera_multiplicity_2009 for details. 
```{r regression of mean on sd}
# FL: variance ~ mean
lm_FL <- lm(FL_var ~ FL_mean, data = trait_stats)
summary(lm_FL)

# FD: variance ~ mean
lm_FD <- lm(FD_var ~ FD_mean, data = trait_stats)
summary(lm_FD)

# B: variance ~ mean
lm_B <- lm(B_var ~ B_mean, data = trait_stats)
summary(lm_B)
```

Make a quick plot to show relationship with flower length as an example.  
```{r regression plot for FL variance and mean}
ggplot(trait_stats, aes(x = FL_mean, y = FL_var)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(title = "Variance scaling for FL", x = "Mean FL", y = "Variance FL")
```
Yes, positive relationship and therefore justification for using CV to describe variability. 

# Functional Regression
As a comparison to standardized linear selection estimates, the following employs functional regression to estimate selection along gradients of within-individual floral variation. We used scalar-on-function regression, with total number of seeds as a scalar response variable, and thin-plate spline functions to describe floral-trait gradients as explanatory variables. To facilitate variation in total flower number across individual plants, we employed the variable domain function in the package `Refund`. 

## Mean traits per flowering day
As an initial analysis, mean values were calculated for all three traits for each day of the flowering period (day 1-17). These means would approximate what a pollinator would encounter on each day of flowering, including the mean change in floral traits. 

```{r mean traits by flowering day}
means.ind <- data %>%
  group_by(PlantID, flw_date) %>%
  summarise(
    mean_FL = mean(FL, na.rm = TRUE),
    sd_FL = sd(FL, na.rm = TRUE),
    var_FL = var(FL, na.rm = TRUE),
    
    
    mean_FD = mean(FD, na.rm = TRUE),
    sd_FD = sd(FD, na.rm = TRUE),
    var_FD = var(FD, na.rm = TRUE),
    
    
    mean_B = mean(B, na.rm = TRUE),
    sd_B = sd(B, na.rm = TRUE),
    var_B = var(B, na.rm = TRUE),
    
    
    mean_flw_vol = mean(flw_vol, na.rm = TRUE),
    sd_flw_vol = sd(flw_vol, na.rm = TRUE),
    var_flw_vol = var(flw_vol, na.rm = TRUE),
    
    
    .groups = "drop"
  )

mn<- as.data.frame(means.ind)
```

Now plot to visualize change. Just showing plot for banner height to save space.
```{r plot means over time}
#Banner
ggplot(mn, aes(x = flw_date, y = mean_B, group = PlantID, color = PlantID)) +
  geom_line(size = 1) +
  geom_ribbon(aes(ymin = mean_B - sd_B, ymax = mean_B + sd_B, fill = PlantID), alpha = 0.2, color = NA) +
  labs(
    x = "Day of Flowering Season",
    y = "Mean Banner Height ± SD",
    title = "Banner Height Over Time by Plant"
  ) +
  theme_minimal() +
  theme(legend.position = "none")  # hides legend
```

## Functional regression on mean traits


# References
